Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-20 1607 - JMC for g2/Paper/JMC_dis.tex
Some ideas jotted down as discussed these last days

\begin{itemize}
\item large-$x$: bridges Braun's pure twist-3 theory and the data
\item smaller-$x$: constrains the small-$x$ behavior of transversity.
\item in general, $g_2^{\text{quark}}$ is quite smaller than the other contribution, as customarily assumed.
\end{itemize}

Another consequence of the new chiral odd term induced by the non-vanishing of
the chiral condensate on the non perturbative vacuum is that the
Burkardt-Cottingham sum rule is broken: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) \ ,
\end{align}
where the integral over $h_1$ is related to target's tensor charge.
Consequences:
\begin{itemize}
\item Inclusive DIS become sensitive to the tensor charge; furthermore, teh BC summ rule isolates the effects due to the chiral odd part of the jet correlator. 
\item Both the jet mass $\mj$ and the tensor charge can in principle be calculated on the lattice
\item Comparison to the Burkhardt-Cottingham sum rule can provide experimental verification of lattice calculation
\item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
\end{itemize}

@@

\section{Conclusions}

\noindent
------------------------------------------------- \\
Edited down to here\\
--------------------------------------------------\\

>>>>

\begin{itemize}
\item large-$x$: bridges Braun's pure twist-3 theory and the data
\item smaller-$x$: constrains the small-$x$ behavior of transversity.
\item in general, $g_2^{\text{quark}}$ is quite smaller than the other contribution, as customarily assumed.
\end{itemize}
Some ideas to check:
\begin{itemize}
\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x. Can we use this to highlight teh $g_2^{jet}$ contribution?
\item In Jam 13, Fig. 6, it looks like in general the violation of teh BC sum rule is a small-x effect --> constraints on h(x) fits? This cannot really be checked vs. JAM15, that assumes $g_2^(0)$ respects BC. 
\end{itemize}

Another consequence of the new chiral odd term induced by the non-vanishing of
the chiral condensate on the non perturbative vacuum is that the
Burkardt-Cottingham sum rule is broken: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) 
    =  \frac{\mj-\mq}{\Lambda} g_T \ ,
\end{align}
where the integral over $h_1$ is related to target's tensor charge $g_T$.
Consequences:
\begin{itemize}
\item Inclusive DIS become sensitive to the tensor charge; furthermore, teh BC summ rule isolates the effects due to the chiral odd part of the jet correlator. 
\item Both the jet mass $\mj$ and the tensor charge can in principle be calculated on the lattice
\item Comparison to the Burkhardt-Cottingham sum rule can provide experimental verification of lattice calculation
\item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
\item Recent calcs of $g_T^{d-u}$ tensor charge are very precise - can we use this info in our plots? (to ``measure'' the quark condenstae $\langle0|\psi\bar\psi|0\rangle>$, for example? this would need an estimate of teh BC breaking, that is only availbal efrom JAM13, for all that I know.)
\end{itemize}

@@
